Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-27 manuscript/ERL_global_C_review.Rmd
Update ERL_global_C_review.Rmd

**check this with final data (based on Table 1):**
There were sufficient data to assess mature forest biome differences for **9** stock variables, and significant differences among biomes were detected for **6** variables (**$B_{tot}$, $B_{ag}$, $B_{ag-wood}$, $B_{foliage}$, $B_{root-coarse}$, $DW_{tot}$**; Table 1).
C stocks had less consistent patterns across biomes (Figs. 7, S16-S26).
In **four of the six** cases (**$B_{tot}$, $B_{ag-wood}$,  $B_{root-coarse}$, $DW_{tot}$**), temperate conifer forests were in the highest significance grouping, and boreal forests in the lowest, with tropical and temperate broadleaf forests  in between--most commonly being significantly different from temperate conifer but not boreal forests.
For $B_{ag}$, which had by far the highest sample size, tropical forests exceeded temperate conifer forests (but not significantly). 
For $B_{foliage}$,temperate broadleaf forests were lowest (again, not significantly).
Once again, the high values for the temperate conifer biome were driven by the very high-biomass forests of the US Pacific Northwest, which are disproportionately represented in the current version of ForC.
Thus, biome differences should be interpreted more as driven more by geographic distribution of sampling than by true differences.

>>>>

**check this with final data (based on Table 1):**
There were sufficient data to assess mature forest biome differences for **9** stock variables, and significant differences among biomes were detected for **6** variables (**$B_{tot}$, $B_{ag}$, $B_{ag-wood}$, $B_{foliage}$, $B_{root-coarse}$, $DW_{tot}$**; Table 1).
C stocks had less consistent patterns across biomes (Figs. 7, S16-S26).
In **four of the six** cases (**$B_{tot}$, $B_{ag-wood}$,  $B_{root-coarse}$, $DW_{tot}$**), temperate conifer forests were in the highest significance grouping, and boreal forests in the lowest, with tropical and temperate broadleaf forests  in between--most commonly being significantly different from temperate conifer but not boreal forests.
For $B_{ag}$, which had by far the highest sample size, tropical forests exceeded temperate conifer forests (but not significantly). 
For $B_{foliage}$,temperate broadleaf forests were lowest (again, not significantly).
The high values for the temperate conifer biome were driven by the very high-biomass forests of the US Pacific Northwest, which are disproportionately represented in the current version of ForC.
Thus, biome differences should be interpreted more as driven more by geographic distribution of sampling than by true differences.
